Title

### 2012-05-03 inc/ms_model/ms_model.tex
nearly completed the inclusion of M&S AG derivation

The $K^{force}$ integrals, related to the internal force of the pulse's Coulombic repulsion, are far more complicated to evaluate.
For more information about the derivation, see \cite{michalik_analytic_2006}.
The final matrices are
\begin{equation}
  K^{force} = 
  \begin{pmatrix}
    k^{force}_{\smallT} & 0 & 0 \\
    0 & k^{force}_{\smallT} & 0 \\
    0 & 0 & k^{force}_{z}
  \end{pmatrix}
\end{equation}
where
\begin{equation}
  k^{force}_{\alpha} = 
  \frac{N e^2}{4\pi\varepsilon_0} \frac{1}{2\pi^{1/2}\sigma_{\alpha}^{1/2}} L_{\alpha}(\xi)
  \begin{pmatrix}
    0 & 1 \\
    1 & \dfrac{2 \gamma_{\alpha}}{\sigma_{\alpha}}
  \end{pmatrix}
\end{equation}
The parameter $\xi$ is the ellipticity parameter, defined as
\begin{equation}
  \xi \equiv \sqrt{\dfrac{\sigma_{z}}{\sigma_{\smallT}}}
\end{equation}
Note that the original paper of Michalik and Sipe contained an error which incorrectly defined $\xi$; this was corrected in an erratum\cite{michalik_erratum:_2008}.
The family of $L$ functions are
\begin{gather}
  L_{\smallT}(\xi) = \frac{3}{2} \left( L(\xi) + \frac{\xi^2 L(\xi) - \xi}{ 1 - \xi^2 } \right) \\
  L_{z}(\xi) = \frac{ 3 \xi^2 }{ \xi^2 - 1} \left( \xi L(\xi) - 1 \right) \\
  L(\xi) = \frac{1}{2} \int_0^{\pi} \frac{1}{1+\xi\sin(\theta)} d\theta
\end{gather}

@@

The results of the previous analyses culminate in the differential equation set
\begin{subequations} \label{eq:ag_original}
\begin{gather}
  \frac{d\sigma_{\alpha}}{dt} = \frac{2\gamma_{\alpha}}{m} \\
  \frac{d\gamma_{\alpha}}{dt} = \frac{1}{m} \left(\eta_{\alpha} + \frac{\gamma_{\alpha}^2}{\sigma_{\alpha}} \right) 
    + \frac{N e^2}{4\pi\varepsilon_0} \frac{1}{6 \sqrt{\sigma_{\alpha}\pi}} L_{\alpha}(\xi)\\
  \frac{d\eta_{\alpha}}{dt} = - \frac{2 \gamma_{\alpha} \eta_{\alpha}}{m \sigma_{\alpha}}
\end{gather}
\end{subequations}
which depends on the ellipticity parameter
\begin{equation}
  \xi \equiv \sqrt{\dfrac{\sigma_{z}}{\sigma_{\smallT}}}
\end{equation}

>>>>

The $K^{force}$ integrals, related to the internal force of the pulse's Coulombic repulsion, are far more complicated to evaluate.
For more information about the derivation, see \cite{michalik_analytic_2006}.
The final matrices are
\begin{equation}
  K^{force} = 
  \begin{pmatrix}
    k^{force}_{\smallT} & 0 & 0 \\
    0 & k^{force}_{\smallT} & 0 \\
    0 & 0 & k^{force}_{z}
  \end{pmatrix}
\end{equation}
where
\begin{equation}
  k^{force}_{\alpha} = 
  \frac{N e^2}{4\pi\varepsilon_0} \frac{1}{2\pi^{1/2}\sigma_{\alpha}^{1/2}} L_{\alpha}(\xi)
  \begin{pmatrix}
    0 & 1 \\
    1 & \dfrac{2 \gamma_{\alpha}}{\sigma_{\alpha}}
  \end{pmatrix}
\end{equation}
The parameter $\xi$ is the ellipticity parameter, defined as
\begin{equation}
  \xi \equiv \sqrt{\dfrac{\sigma_{z}}{\sigma_{\smallT}}}
\end{equation}
Note that the original paper of Michalik and Sipe contained an error which incorrectly defined $\xi$; this was corrected in an erratum \cite{michalik_erratum:_2008}.
The family of $L$ functions are
\begin{gather}
  L_{\smallT}(\xi) = \frac{3}{2} \left( L(\xi) + \frac{\xi^2 L(\xi) - \xi}{ 1 - \xi^2 } \right) \\
  L_{z}(\xi) = \frac{ 3 \xi^2 }{ \xi^2 - 1} \left( \xi L(\xi) - 1 \right) \\
  L(\xi) = \frac{1}{2} \int_0^{\pi} \frac{1}{1+\xi\sin(\theta)} d\theta
\end{gather}
The integral function $L(\xi)$ can be evaluated to the piecewise function
\begin{equation}
  L(\xi) = 
  \begin{cases}
    \frac{ \arcsin \sqrt{1-\xi^2} }{ \sqrt{1-\xi^2} } & 0 \le \xi \le 1 \\
    \frac{ \ln\left( \xi + \sqrt{\xi^2 - 1} \right) }{ \sqrt{\xi^2 - 1} } & \xi \ge 1
  \end{cases}
\end{equation}
which, although piecewise, is a smooth and well behaved function.

@@

The results of the previous analyses culminate in the differential equation set
\begin{subequations} \label{eq:ag_original}
\begin{gather}
  \frac{d\sigma_{\alpha}}{dt} = \frac{2\gamma_{\alpha}}{m} \\
  \frac{d\gamma_{\alpha}}{dt} = \frac{1}{m} \left(\eta_{\alpha} + \frac{\gamma_{\alpha}^2}{\sigma_{\alpha}} \right) 
    + \frac{N e^2}{4\pi\varepsilon_0} \frac{1}{6 \sqrt{\sigma_{\alpha}\pi}} L_{\alpha}(\xi)\\
  \frac{d\eta_{\alpha}}{dt} = - \frac{2 \gamma_{\alpha} \eta_{\alpha}}{m \sigma_{\alpha}}
\end{gather}
